The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2012-01-30 bmc_article.tex
Writing up coding standards...

@@

>>>>

As the library grew over the years, so did the maintenance become more complex. Increasingly,
the main branch did not compile, and bug fixing become increasingly difficult, as fixing a bug
in one part of the code, broke some other code which made the wrong assumption about the first
code.

To address these issues, we have adopted a number of coding standards. By no means there are
meant to implement the best practices of source code development; instead, they attempt to find
a balance between increasing code maintainability and being flexible enough to allow efficient
code development. However, we appreciate the subjective nature of this statement, and some
adopted guidelines have been heavily discussed in the community.
The next sections describe some approaches the project have adopted that allows us to
maintain the CDK library as it is today.

One of the key approaches we have adopted, is to make the CDK more modular. The CDK assigns
every class to a module, and defines dependencies between modules. For example, core modules
are not allowed to depend on a module holding data classes implementing the CDK interfaces;
instead, they may only depend on the interfaces themselves. This, for example, is to ensure
that dependencies are minimized and to make it easier to exclude CDK functionality with
third-party dependencies that are not needed.

... describe all modules, maybe add graphviz plot ...

@@

Another big changes since the CDK 1.2 series, is that the project adopted a peer-review
step in its development. New functionality is now developed independently from the main
CDK library until it is finished. When it is finished, the new code is send around to
other developers to be reviewed, very much like how research papers are peer-reviewed
by journals before publication. Independent developers review the code to check if it 
meets our community's standards.
